### 2013-07-24 Chap2(NV).tex
updated for Ian to change

\chapter{Current Methods in Processing SAR and POLSAR Data} %chapter 2
\label{chap:lit_survey}

@@

\subsection{The Stochastic Nature of SAR data}

@@

SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
  each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
The random nature of the SAR data arises
  due to the unknown and varying location, height and thus distance of each elementary scatterer;
  which, in turn, generates random phases in their back-scattering responses.
Assuming the number of these elementary back scatterers is sufficiently large,
  then the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}.
Consequently the interference of these randomly phased responses can be considered as
  a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  
Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. 
Their probability density functions (PDF) are given as:

@@

%\begin{eqnarray}
%pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
%pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
%\end{eqnarray}
\begin{equation}
\label{eqn:SAR Amplitude PDF}
\caption{eqn:SAR Amplitude PDF}
pdf(A) = \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }
\end{equation}
\begin{equation}
  \label{eqn:SAR Intensity PDF}
  \caption{eqn:SAR Intensity PDF}
pdf(I) = \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
\end{equation}

@@

%The stochastic nature SAR arises from the speckle phenomena.
As SAR speckle phenomena arises from the stochastic nature of SAR, it seriously hinders the interpretation and understanding of SAR images.
Speckle noise on SAR images are hence routinely reduced through a speckle filtering process for easier human interpretation and more accurate post-processing.
%***IVM: Hai, I added "human" before 'interpretation'. Also added the text afterwards, please check that the sense of the edited text is still correct in terms of what you wanted to say.

@@

\subsubsection{The polarization property of Electro-Magnetic waves}

The propagation of Electro-Magnetic (EM) wave in space is governed by Maxell‚Äôs equations. 
The general solution to these equations is a linear superposition of waves, each having the form of:
\begin{eqnarray*}
 \vec{E}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r}) \\
 \vec{B}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
\end{eqnarray*}
where
	$g$ is any well-behaved function of a dimensionless argument $\phi$,
	%for virtually any¬†well-behaved function g¬†of dimensionless argument œÜ, where
	$\omega$ is the angular frequency (in radians per second), and
	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).

Because of the divergence between the electric and the magnetic fields, there will be no fields in the direction of wave propagation.
Thus if we define the z direction as the travelling direction of the EM wave,
  then both the electric and the magnetic fields are fluctuating in the x,y plane.
Furthermore, when considering wave propagation, it is conventional that only the electric field vector is described and the magnetic field is ignored since it is perpendicular to the E field and is proportional to it.
Projecting this vector into x,y directions, we have:

\begin{equation*}
\vec{E}(z,t) 
= 
\left(
	\begin{array} {c}
		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
		0
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		\xi_x(t) \\
		\xi_y(t) \\
		0
	\end{array}
\right)
\end{equation*}
where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.

In other words, the EM vector can oscillate in more than one orientation, and this denote the polarization property of EM wave.
The exact shape traced out in a fixed projective plane by the tip of the electric vector as the plane propagate is a description of the polarization state.
This shape is characterized by the formula: 
\begin{equation*}
 \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
\end{equation*}
where
	$\Delta \phi = \phi_y^0 - \phi_x^0$
The formula characterizes what is termed as the polarization ellipse.

The parameters that describe the polarization ellipse are: 
\begin{equation*}
\tan (\theta ) = \frac{E_y^0}{E_x^0}
\end{equation*}
with
	$0 \leq \theta \leq \pi/2$. 
The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
\begin{equation*}
\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
\end{equation*}
with
	$0 \leq \Psi < \pi$. 
The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
\begin{equation*}
\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
\end{equation*}
with
	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$

Ignoring the scale of the electrical fields, the elementary wave polarization can be completely described by two parameters, i.e. $E_y^0/E_x^0$ and $\Delta \phi = \phi_y^0 - \phi_x^0$. 
Similarly, ignoring the scale of the ellipse, the polarization ellipse can be completely described by two angles $\Psi$ and $\chi$.

Other parameters includes:
\paragraph{ Complex polarization ratio }
This ratio is important in explaining polarization basis changes.

It is defined as:
\begin{equation}
\rho = \frac{E_y^0}{E_x^0} e^{i \Delta \phi} = \frac{\cos(2 \chi) + i \sin(2 \chi)}{1 - \cos(2\Psi) \cos(2\chi)}
\end{equation}

\paragraph{Jones Vector}

%Let the total wave power:
%\begin{equation}
%|E|^2 = (E_x^0)^2  + (E_y^0)^2
%\end{equation}
%and phase 
%\begin{equation}
%\theta = \tan^{-1} \left( \frac{E_y^0}{E_x^0} \right)
%\end{equation}

The Jones vector is defined as 
\begin{equation}
J = 
\left(
\begin{array}{c}
	\xi_x(t) \\
	\xi_y(t) 
\end{array}
\right)
= \xi_x(t)
\left(
\begin{array}{c}
	1 \\
	\rho
\end{array}
\right)
\end{equation}

Thus the normalized Jones vector can be given as:
\begin{equation}
J = 
\left(
\begin{array}{c}
	\cos(\theta) \cdot e^{i \phi_x^0} \\
	\sin(\theta) \cdot e^{i \phi_y^0}
\end{array}
\right)
=
\left(
\begin{array}{c}
	1\\
	\tan(\theta) \cdot e^{i \Delta \phi}
\end{array}
\right)
=
\left(
\begin{array}{c}
	\cos(\Psi) \cos(\chi) - i \sin(\Psi) \sin(\chi) \\
	\sin(\Psi) \cos(\chi) + i \cos(\Psi) \sin(\chi)
\end{array}
\right)
\end{equation}

The two parameters in the Jones vector can completely describe the polarization state (ellipse) of any elementary wave.
This same Jones vector finds extensive use in quantum machenics, and is interpreted as quantum state vector.
Its bra-ket notation formula, which is normally used in quantum computation contexts is:
\begin{equation}
J = | \Psi \rangle 
= 
\left(
\begin{array}{c}
	\cos(\theta) \cdot e^{i \phi_x^0} \\
	\sin(\theta) \cdot e^{i \phi_y^0}
\end{array}
\right)
\end{equation}

By definitions, the horizontal linear polarized wave is defined as: $J_h = \left(
\begin{array}{c}
 1 \\
 0
\end{array}
\right)$, similarly the vertical linear polarized wave: $J_v = \left(
\begin{array}{c}
 0 \\
 1
\end{array}
\right)$, the $\pm \pi/4$ linear polarized waves $J_{\pm} = \pm \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 1
\end{array}
\right)$, the left circular polarized wave: $J_l = |L\rangle = \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 -i
\end{array}
\right)$ and the right circular polarized wave: $J_r = |R\rangle = \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 i
\end{array}
\right)$

\paragraph{ Stokes Vector}

Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
The wave coherency matrix is defined as:
\begin{equation*}
W_c = \left<
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)^{\dagger}
\right>
= \left<
\left(
\begin{array}{c c}
 \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
 \xi_y \xi_x^* 	& \xi_y \xi_y^* 
\end{array}
\right)
\right>
= \left<
\left(
\begin{array}{c c}
 |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
 |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
\end{array}
\right)
\right>
\end{equation*}

The Stokes vector is then defined as:
\begin{equation*}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation*}

In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
\begin{equation*}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_0 \cos(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\chi)
\end{array}
\right)
\end{equation*}

@@

At this point, a distinction needs to be highlighted. %explaination is warranted.
%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
In comparison to the two-element Jones vector, Stokes vectors have more data, namely four elements. 
The Jones vector can completely describe the polarization states of an elementary wave, whose formulation is based on the assumption that the wave is very well behaved.
In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
As such, the polarization of the waves are normally not fully polarized.
One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
%The phenomena can be loosely called wave depolarization. %****IVM: Hai, is this your term or is it also used by others for the same thing? In that case, it might be good to put a reference here. I think the word "loosely" is one of those trigger words that causes the examiner to sit up and read it critically.

@@

%(comment: I think it would be better if you can link the two paragraphs together, such as
%ìClosely related to the Stoke vector is the concept of Degree of polarization p, which is a quantity used to describeÖî, or something like this )

@@

Closely related to the Stokes vector is the concenpt of ``Degree of polarization'' $p$, which is a quantity used to describe the portion of an EM wave which is polarized.
A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
Thus $0 \leq p \leq 1$.

@@

In fully polarized wave, the following equation holds:
\begin{equation*}
S_0^2 = S_1^2 + S_2^2 + S_3^2
\end{equation*}

In depolarized wave, it becomes an in-equation
\begin{equation*}
S_0^2 > S_1^2 + S_2^2 + S_3^2
\end{equation*}

Then the degree of polarization is defined as
\begin{equation*}
p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
\end{equation*}

In such general case, the Stokes Vector is written as:
\begin{align*}
S_t &= 
\left(
\begin{array}{c}
 I \\
 I p \cos(2\Psi) \cos(2\chi) \\
 I p \sin(2\Psi) \cos(2\chi) \\
 I p \sin(2\chi)
\end{array}
\right) \\
 &= I (1 - p)
\left(
\begin{array}{c}
 1 \\
 0 \\
 0 \\
 0
\end{array}
\right) 
+ I p
\left(
\begin{array}{c}
 1\\
 \cos(2\Psi) \cos(2\chi) \\
 \sin(2\Psi) \cos(2\chi) \\
 \sin(2\chi)
\end{array}
\right)
\end{align*}

Alternatively, if the Stokes vector is measured and known, then the polarization characteristics of a wave are given as:
$I$, the total power of the measured beam is $I=S_0$,
$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.

@@

POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
\begin{equation*}
 E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
\end{equation*}
%***IVM: Hai, do you need to explain the k & r terms?

Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
\begin{equation*}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c c}
 S_{HH} & S_{HV} \\
 S_{VH} & S_{VV}
\end{array}
 \right) 
\left( 
\begin{array}{c}
 E_h^{Tx} \\
 E_v^{Tx}
\end{array}
 \right) 
\end{equation*}

The scattering matrix can be called the Jones matrix (relating to the Jones vector) in the forward scattering alignment.
The matrix is normally called the Sinclair matrix in SAR literature, as backward scattering alignment is normally adopted for SAR \cite{Sinclair_1950_ProcsIRE}.
In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \cite{Nghiem_1992_RadioSci}.

The matrix can also be ``stratified'' to define the target scattering vector as: 
\begin{equation}
  \label{eqn:Covariance Target Vector of Full Polarimetric SAR}
  \caption{eqn:Covariance Target Vector of Full Polarimetric SAR}
T_{cv} = \left( 
\begin{array}{c}
 S_{HH} \\
 \sqrt{2} S_{HV} \\
 S_{VV}
\end{array}
 \right) 
\end{equation}
or 
\begin{equation}
  \label{eqn:Coherence Target Vector of Full Polarimetric SAR}
  \caption{eqn:Coherence Target Vector of Full Polarimetric SAR}
T_{ch} = \frac{1}{\sqrt{2}} \left( 
\begin{array}{c}
 S_{HH} + S_{VV}\\
 S_{HH} - S_{VV} \\
 S_{HV}
\end{array}
 \right) 
\end{equation}

>>>>

\chapter{Current Methods in Processing SAR and POLSAR Data} %chapter 2

@@

\subsection{The Stochastic nature of SAR data}

@@

SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
  each reflecting from different and distributed elementary scatterers \citep{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
The random nature of the SAR data arises
  due to the unknown and varying location, height and thus distance of each elementary scatterer;
  which, in turn, generates random phases in their back-scattering responses.
Assuming the number of these elementary back scatterers is sufficiently large,
  then the Central Limit Theorem is applicable \citep{Goodman_Springer_1975}.
Consequently the interference of these randomly phased responses can be considered as
  a random walk on the 2D complex plane \citep{Goodman_JOptSocAm_76}.  
Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \citep{Lee_CRCPress_2009}. 
Their probability density functions (PDF) are given as:

@@

\begin{eqnarray}
pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
\end{eqnarray}

@@

%The stochastic nature SAR arises from the speckle phenomena.
As SAR speckle phenomena arises from the stochastic nature of SAR, it seriously hinders the interpretation and understanding of SAR images.

Speckle noise on SAR images are hence routinely reduced through a speckle filtering process for easier human interpretation and more accurate post-processing.
%***IVM: Hai, I added "human" before 'interpretation'. Also added the text afterwards, please check that the sense of the edited text is still correct in terms of what you wanted to say.

@@

%***IVM: Hai your citations are wrong in this paragraph, they should be \citep (I think I've fixed them all though)
Early works from the radar community had focused on the theoretical introduction of the scattering matrix such as the Sinclair matrix or Mueller matrices, for full, i.e. quad, polarimetric measurements \citep{Sinclair_1950_ProcsIRE}.
%(Sinclair, 1950), (TODO) 
These works were continued by Boerner, and the first polarimetric images were captured by NASA JPL at Caltech in 1991 \citep{Zebker_1991_ProcsIEEE}.

Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat, TerraSAR, Alos-PalSAR were launched.
However due to operational restrictions on payload, power and data-downlink (speed?), the satellites also offer dual-channel polarimetric SAR modes as a compromise between theoretical polarimetric requirements and practical limitations.
Initially, to the end user, while dual-channel partial polarimetry may not provide the complete polarimetric signature of the target, the loss is compensated for by either better resolutions or higher coverage and lower cost.  (Comment - this sentence is not clear to me. How does the ëlossí be compensated by ëbetter resolutionsí? I thought loss means the resolution becomes worse to start with)

Until very recently, these partial polarimetry modes were not formally taken up by scientists and academia. 
In his pioneer paper in 2005, Souyris\citep{Souyris_2005_TGRS} introduced the so-called compact polarimetry mode and suggested that it may be possible to reconstruct full polarimetric information from compact polarimetric data.
Raney\citep{Raney_2006_IGARSS} also showed that dual-channel polarimetry is not only capable of measuring the complete polarization information of the back-scattered EM wave (via Stokes parameters), it is also capable of detecting the basic target's polarimetric characteristic, e.g. odd or even bounce phenomena.

While the dual-polarization mode sensing has been available operationally for quite some time, partial polarimetry has only recently been investigated in the scientific community. 
In comparison, 
	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
	while full polarimetry measures the same response from two (generally orthogonal) polarisation channels.
Mathematically, the process is modelled as:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c}
 S_{H} \\
 S_{V}
\end{array}
 \right) E^{Tx}
\end{equation}

%****IVM: Hai, the equation doesn't fit - can you do something like this instead? (and same for the next eqn too)-> 
\begin{equation}
J = 
\left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 }              		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
	{+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
\vspace{0.1}
	{s_{HH}^*s_{VV} + |s_{HV}|^2}         		& 	{|s_{VV}|^2 + |s_{HV}|^2}\\
	{+ s_{HV}s_{HH}^* + s_{VV}s_{HV}^*} 	& { + 2 \Re{(s_{VV}s_{HV}^*)}}
\end{array}
\right)
\end{equation}

%*** IVM, I changed the following reference to a \citet
\citet{Raney_2006_IGARSS} demonstrated a different perspective by proposing a hybrid architecture.
He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
The important parameter is the choice of the polarisation to be used for the incoming pulse.
His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
The partial covariance matrix then becomes:
\begin{equation}
J = \frac{1}{2} \left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* - i (|s_{HV}|^2 + s_{HH}s_{VV}^*)\\
	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
& 	|s_{VV}|^2 + |s_{HV}|^2 + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)
\end{array}
\right)
\end{equation}

(Comment: check the presentation of this equation in the pdf file)

The benefits of this hybrid architecture, according to Raney are that it can measure certain physical polarimetric phenomena such as the odd and even bounce phenomena.
The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
\begin{equation}
\Gamma_{tri} = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right)
\end{equation}
Then the response will be reversed as it can be calculated as:
\begin{equation}
J_r = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
i
\end{array}
\right) 
\end{equation}
with
	$ \left( \begin{array}{c} 1 \\ -i \end{array} \right) $ indicating right circular polarization transmitted, and
	$ \left( \begin{array}{c} 1 \\ i \end{array} \right) $ indicating left circular polarization received.

For a dihedral target, whose main axis is at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
\begin{equation}
\Gamma_{dih} = 
\left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right)
\end{equation}
The even bounce phenomena is detectable as its polarimetric response, which is then:
\begin{equation}
J_r = \left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) 
\end{equation}
In \citep{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conveniences to hardware calibration.
Also in a follow up study \citep{Raney_2007_TGRS}, he demonstrated the classification power of hybrid polarimetry.
Furthermore, Lardeux \citep{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
Notably, the hybrid architectural concept has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \citep{Raney_2009_RadarConf}.

The research into partial polarimetry is convenient as its data can be simulated using polarisation basis transformations such as those described above.
Hardware realisation may not be needed until the final physical prototype stages.
This methodology has been demonstrated and is widely used in the community.
We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
The focus into partial polarimetry allows analysis with a smaller matrix, while its implications can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
Besides that, a number of research questions in this new field are still open, relevant and exciting.

Souyris, in 2005, published a paper \citep{Souyris_2005_TGRS} which claimed and presented an algorithm to reconstruct full polarimetric information from the given partial compact polarimetric data.
The algorithm is claimed to work on natural surfaces.
In \citep{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given. %****IVM: Hai are Nord / Ainsworth single author? If not, you need an "et. al."
In \citep{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
Chapter 3 will review this sub-topic further and introduce our work on expanding the reconstruction to urban man-made structures and surfaces (from the original system which was relevant to natural cover only).

For the tasks of target detection and classification, we believe that partial dual polarization provides a unique proposition.
Compared with single-channel systems, the dual channel provides additional and useful polarimetric information. 
Compared with full polarimetric data, the better spatial resolution of dual channel systems could compensate for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.
\paragraph{ Stokes Vector}

Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
The wave coherency matrix is defined as:
\begin{equation}
W_c = \left<
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)^{\dagger}
\right>
= \left<
\left(
\begin{array}{c c}
 \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
 \xi_y \xi_x^* 	& \xi_y \xi_y^* 
\end{array}
\right)
\right>
= \left<
\left(
\begin{array}{c c}
 |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
 |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
\end{array}
\right)
\right>
\end{equation}

The Stokes vector is then defined as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation}

In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_0 \cos(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\chi)
\end{array}
\right)
\end{equation}

@@

At this point, a distinction needs to be highlighted. %explaination is warranted.
%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
In comparison to the two-element Jones vector, Stokes vectors have more data, namely four elements. 
The Jones vector can completely describe the polarization states of an elementary wave, whose formulation is based on the assumption that the wave is very well behaved.
In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
As such, the polarization of the waves are normally not fully polarized.
One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
The phenomena can be loosely called wave depolarization. %****IVM: Hai, is this your term or is it also used by others for the same thing? In that case, it might be good to put a reference here. I think the word "loosely" is one of those trigger words that causes the examiner to sit up and read it critically.

@@

(comment: I think it would be better if you can link the two paragraphs together, such as
ìClosely related to the Stoke vector is the concept of Degree of polarization p, which is a quantity used to describeÖî, or something like this )

@@

Degree of polarization $p$ is a quantity used to describe the portion of an EM wave which is polarized.
A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
Thus $0 \leq p \leq 1$.

@@

In fully polarized wave, the following equation holds:
\begin{equation}
S_0^2 = S_1^2 + S_2^2 + S_3^2
\end{equation}

In depolarized wave, it becomes an in-equation
\begin{equation}
S_0^2 > S_1^2 + S_2^2 + S_3^2
\end{equation}

Then the degree of polarization is defined as
\begin{equation}
p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
\end{equation}

In such general case, the Stokes Vector is written as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 I \\
 I p \cos(2\Psi) \cos(2\chi) \\
 I p \sin(2\Psi) \cos(2\chi) \\
 I p \sin(2\chi)
\end{array}
\right)
 = I (1 - p)
\left(
\begin{array}{c}
 1 \\
 0 \\
 0 \\
 0
\end{array}
\right) 
+ I p
\left(
\begin{array}{c}
 1\\
 \cos(2\Psi) \cos(2\chi) \\
 \sin(2\Psi) \cos(2\chi) \\
 \sin(2\chi)
\end{array}
\right)
\end{equation}

Alternatively, if the Stokes vector is measured and known, then the polarization characteristics of a wave are given as:

(Comment: the following should be re-aligned into multiple equations, instead of one long sentence ñ see pdf file)

$I$, the total power of the measured beam is $I=S_0$,
$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.

(comment: you should link the following paragraph to the above discussion ñ I suggest move the following paragraph to earlier as shown here)

@@

POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
\begin{equation}
 E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
\end{equation}
%***IVM: Hai, do you need to explain the k & r terms?

Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c c}
 S_{HH} & S_{HV} \\
 S_{VH} & S_{VV}
\end{array}
 \right) 
\left( 
\begin{array}{c}
 E_h^{Tx} \\
 E_v^{Tx}
\end{array}
 \right) 
\end{equation}

The scattering matrix can be called the Jones matrix (relating to the Jones vector) in the forward scattering alignment.
The matrix is normally called the Sinclair matrix in SAR literature, as backward scattering alignment is normally adopted for SAR \citep{Sinclair_1950_ProcsIRE}.
In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \citep{Nghiem_1992_RadioSci}.

The matrix can also be ``stratified'' to define the target scattering vector as: 
\begin{equation}
T_{cv} = \left( 
\begin{array}{c}
 S_{HH} \\
 \sqrt{2} S_{HV} \\
 S_{VV}
\end{array}
 \right) 
\end{equation}
or 
\begin{equation}
T_{ch} = \frac{1}{\sqrt{2}} \left( 
\begin{array}{c}
 S_{HH} + S_{VV}\\
 S_{HH} - S_{VV} \\
 S_{HV}
\end{array}
 \right) 
\end{equation}

Similar to the reason that Stokes vectors are preferred to Jones vector in wave polarization, 
	second order statistics of the target scattering matrix are normally preferred.
The covariance matrix is defined as:
\begin{equation}
\small{
C_v = \left< T_{cv} T_{cv}^{*T} \right> = 
\left( 
\begin{array}{c c c}
 S_{HH}S_{HH}^* 	& \sqrt{2}S_{HH}S_{HV}^*	& S_{HH}S_{VV}^* \\
 \sqrt{2}S_{HV}S_{HH}^* & 2 S_{HV}S_{HV}^* 		& \sqrt{2}S_{HV}S_{VV}^* \\		
 S_{VV}S_{HH}^*		& \sqrt{2}S_{VV}S_{HV}^*	& S_{VV}S_{VV}^*
\end{array}
 \right) 
}
\end{equation}
while the coherency matrix is defined as:
\begin{equation}
\small{
C_h = \left< T_{ch} T_{ch}^{*T} \right> = \frac{1}{2}
\left( 
\begin{array}{c c c}
 (S_{HH}+S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}+S_{VV})(S_{HH}-S_{VV})^*	& (S_{HH}+S_{VV})S_{HV}^* \\
 (S_{HH}-S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}-S_{VV})(S_{HH}-S_{VV})^* 	& (S_{HH}-S_{VV})S_{HV}^*\\		
 2S_{HV}(S_{HH}+S_{VV})^*		& 2S_{HV}(S_{HH}-S_{VV})^*		& S_{HV}S_{HV}^*
\end{array}
 \right) 
}
\end{equation}
%***IVM: Hai, maybe you can use the small maths font for this matrix... I can't remember the exact syntax, but it's something simple like \small or \mathsmall or similar....

(comment: check layout of the above equation in the pdf file)

Evidently the two matrices are related:
\begin{equation}
C_h = N C_v N^T
\end{equation}
where
	$N = \frac{1}{\sqrt{2}}
\left( 
\begin{array}{c c c}
 1 & 0		& 1\\
 1 & 0		& -1\\
 0 & \sqrt{2}	& 0
\end{array}
\right)$
